Moral Foundations of U.S. Political News Organizations

### 2019-03-04 pilot_manuscript.Rmd
updates

````{r NPR, eval = F, include = F}
url2 = 'https://www.npr.org/search?query=kavanaugh&page=1'
webpage2 = read_html(url2)
headline_data2 = html_nodes(webpage2,'.title .ais-Highlight-nonHighlighted')

@@

  ##save the data
  NPRDF$Source[i] = "NPR"
  NPRDF$Url[i] = urlslist2[i]
  NPRDF$Text[i] = paste(text_data2, collapse = "")
} ##end for loop
```

>>>>

````{r NPR, eval = F, include = F}
urlslist_final = c()

##loop through the page number at the end until done with ~1000 / 20 = 50
for (i in 1:2){ ##change this to 50
  url2 = paste0('https://www.npr.org/search?query=kavanaugh&page=', i)
  webpage2 = read_html(url2)
  headline_data2 = html_nodes(webpage2,'.title')

  #URLs
  attr_data2 = html_attrs(headline_data2) 
  urlslist2 = unlist(attr_data2)
  urlslist2 = urlslist2[grep("http", urlslist2)]

  #add them to an overall
  urlslist_final = c(urlslist_final, urlslist2)

  Sys.sleep(runif(1, 1, 5))
}

##start a data frame
NPRDF = matrix(NA, nrow = length(urlslist_final), ncol = 3)
colnames(NPRDF) = c("Source", "Url", "Text")
NPRDF = as.data.frame(NPRDF)

@@

  ##save the data
  NPRDF$Source[i] = "NPR"
  NPRDF$Url[i] = urlslist2[i]
  NPRDF$Text[i] = paste(text_data2, collapse = "")
  Sys.sleep(runif(1, 1, 5))
} ##end for loop
```
